### 2016-07-10 version0.0/intro0.0.tex
Update intro0.0.tex
edits to first part of SFR section

\section{SFR}
\label{sec: sfr_intro}
Understanding formation of stars leads to understanding galaxies formation and evolution. 
Characterisation of the star formation processes such as SFR and IMF is necessary in examining galaxies structure formation~\citep{McKee07}. 
Measuring the SFR is not trivial and depends on galaxy's morphology, metallicity, IMF, spatial resolution of a target system, and other propertied of galaxies. 
There is a large number of review papers in the literature on how stars form and how their formation is traced. 
From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
From an observational standpoint, star formation is discussed by \cite[][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.

In principle, emission from new stars can be traced by UV emission, optical light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of these emission are directly from stars, e.g UV emission, and some are from ISM components around stars that absorb and re-emit light of young stars, e.g FIR emission.
Techniques to calibrate emission from the newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed were subjects of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08} 
Emission from the young massive type ``O'' or ``B'' stars are normally used as a tracer of the current SFR.
One of the main assumptions for using luminosity of massive stars is that SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing IMF, the number of massive stars can be used to extrapolate the total number of the high and low mass stars that are formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

>>>>

\section{SFR}
\label{sec: sfr_intro}
Understanding the formation of stars leads to better understanding of galaxies' formation and evolution. 
Characterisation of the star formation processes such as star formation rate (SFR) and the stellar initial mass function (IMF) is necessary in examining galaxies' structure formation~\citep{McKee07}. 
Measuring the SFR is not trivial and depends on a galaxy's morphology, metallicity, IMF, observational spatial resolution, and other properties. 
There is a large number of review papers on how stars form and how their formation is traced. 
From a theoretical perspective, one can refer to the classic picture of the theory of star formation as reviewed by \cite{Shu87} and more recently by~\citep{McKee07}. 
From an observational standpoint, star formation is discussed by \cite[][and references therein]{Kennicutt98b, Kewley02, Calzetti13, Boquien10, Kennicutt12}.

In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08} 
Emission from young, massive, type ``O'' or ``B'' stars is normally used as a tracer of the current SFR. %PB: why?
One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.
